%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.0 (14/7/16)
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by 
% Vel (vel@LaTeXTemplates.com) and Harsh (harsh.gadgil@gmail.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{sidebarcv} % a4paper for A4

% Command for printing skill overview bubbles
\newcommand\skills{ 
~
	\smartdiagram[bubble diagram]{
        \textbf{Machine}\\\textbf{Learning},
        \textbf{~~Architecture~~},
        \textbf{~Team~}\\\textbf{Lead},
        \textbf{~~Data~~}\\\textbf{Engineering},
        \textbf{~Full~}\\\textbf{~Stack~}
    }
}

\education{
\textbf{Master of Computer Science } \\
University of Iowa  \\
2008 - 2011 \vspace{2mm}

\textbf{Bachelor of Computer Science } \\
Universidad Católica Boliviana  \\
2008 - 2011
}





%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------
% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}

\cvname{\huge Martin Fabbri} % Your name
\cvjobtitle{\large Lead Machine Learning Engineer} % Job
% title/career

\cvlinkedin{/in/martinfabbri}
\cvgithub{martin-fabbri}
\cvnumberphone{541-232-5000} % Phone number
\cvsite{} % Personal website
\cvmail{martin.fabbri.a@gmail.com} % Email address
\cvlocation{Eugene, OR} % Location

%----------------------------------------------------------------------------------------

\begin{document}

\makeprofile % Print the sidebar

%----------------------------------------------------------------------------------------
%	 SUMMARY
%----------------------------------------------------------------------------------------

\section{Summary}

A Machine Learning Engineer aspirant who is passionate about learning cutting-edge technology and solving real-world problems, currently working with 6 Years experience as a Test Automation Engineer in \textbf{J. P Morgan Chase \& Co.} \\
\begin{twenty}
\twentyitem
{}
{}
{}
{\href{}{}}
{}
{\begin{itemize}
\item Knowledge on machine learning \textbf{Data Processing} steps like Data Exploration, Feature Cleaning, Feature Selection, Feature Encoding to construct a Dataset to apply various machine learning algorithms.
\item Good Knowledge in utilizing various libraries like \textbf{Numpy, Pandas, Matplotlib, Seaborn} to perform various Data Processing steps to develop a model.
\item Knowledge in developing machine learning model using \textbf{Scikit-Learn} library by utlizing various classification, regression and clustering algorithms.
\item Hands-on knowledge on various algorithms like \textbf{Regression, Logistic Regression, Random Forest, Decision Trees, Support Vector Machines, K Nearest Neighbours (KNN), K-Means and Naive Bayes} techniques.
\item Developing my skills by building machine learning models on various data sets available in Kaggle using Python and various libararies mentioned above. 
\end{itemize}}
\\
\end{twenty}


%----------------------------------------------------------------------------------------
%	 Experience
%----------------------------------------------------------------------------------------
\section{Experience}
\begin{twenty}
	\twentyitem
    	{May 2017 -}
		{Present}
        {Access File Services}
        {\href{}{Test Automation Engineer}}
        {}
        {
        {\begin{itemize}
        \item \textbf {Tools Used}: Selenium Web Driver, Jenkins, Maven, Git, BitBucket
        \item Focused on automating test cases using Selenium and Java for various regression tests by also performing Functional testing. 
        \item Identify \& Develop automated test cases to perform PVT tests in production environment.
        \item Took various reponsibilities by exposing myself to various stages of SDLC \& STLC till the last stage to perform End-to-End testing and Product Verification Testing. 
        \item Extensive exposure to various defect management tools like ALM, JIRA for Creating Requirements, Writing Test Cases, Creating Test Sets, Mapping the Requirements and Logging Defects. \vspace{2mm}
		\end{itemize}}
        }
	\twentyitem
    	{Feb 2013 -}
		{Apr 2017}
        {FircoSoft}
        {\href{}{UAT Specialist}}
        {}
        {
        {\begin{itemize}
        \item \textbf {Tools Used}: Selenium Web Driver, Filezilla, Putty
        \item Primarily automated test cases using Selenium on Fircosoft Message Filter UI to perform various regression tests.
        \item Responsible for building rules and lists files using Fircosoft MultiLaws Manager and Fircosoft Multilist Manager respectively and testing them using FFF Classic.
        \item Worked on several Fircosoft tools like FMM, FML, FMF, FFF, FFF Classic, Fircosoft Continuity and was expertise in using these tools to perform various tests related to rules, lists on various payments/transactions.
		\end{itemize}}
        }
\end{twenty}
\end{document} 
